The Changing Face of Pediatric Pulmonary Exacerbations in CF (NACFC 2023)

### 2023-03-29 Scott Sagel/PEx in CF/nacfc_2023.qmd
Update nacfc_2023.qmd

bugs = c("P. aeruginosa","P. aeruginosa mucoid","P. aeruginosa non-mucoid","Staph aureus","MRSA")

@@

@@

```{r}
#| label: tbl-site
#| tbl-cap: Stratified by Site
#| message: false
summ %>%
  select(-`Unique number`) %>%
  tbl_strata(
    strata = Site,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(by=Year,
              type = list(`# of Hospitalizations per Person` ~ 'continuous'),
              statistic = list(
                c("# of Hospitalizations per Person","# Days in Admit") ~ "{median} ({p25}, {p75})",
                c("Age at Admit","Change in FEV1","FEV1 % Predicted at Admit",
                  "FEV1 % Predicted at Discharge") ~ "{mean} ({sd})"
              ),
              missing_text = "(Missing)") %>%
  add_ci(pattern = "{stat} [{ci}]") %>%
  add_p(test = list(
    `Age at Admit`~"t.test",
    `Change in FEV1`~"t.test"
  )) %>%
  separate_p_footnotes()
  ) %>%
  as_gt() %>%
  as_raw_html()
```

>>>>

bugs = c("P. aeruginosa","P. aeruginosa mucoid","P. aeruginosa non-mucoid","Staph aureus","MRSA","S. maltophilia")

@@

df$`S. maltophilia`[df$Site == "CNH"] = NA

@@

```{r}
#| label: tbl-site
#| tbl-cap: Stratified by Site
#| message: false
summ %>%
  select(-`Unique number`,-`S. maltophilia`) %>%
  tbl_strata(
    strata = Site,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(by=Year,
              type = list(`# of Hospitalizations per Person` ~ 'continuous'),
              statistic = list(
                c("# of Hospitalizations per Person","# Days in Admit") ~ "{median} ({p25}, {p75})",
                c("Age at Admit","Change in FEV1","FEV1 % Predicted at Admit",
                  "FEV1 % Predicted at Discharge") ~ "{mean} ({sd})"
              ),
              missing_text = "(Missing)") %>%
  add_ci(pattern = "{stat} [{ci}]") %>%
  add_p(test = list(
    `Age at Admit`~"t.test",
    `Change in FEV1`~"t.test"
  )) %>%
  separate_p_footnotes()
  ) %>%
  as_gt() %>%
  as_raw_html()
```
